---
title: "Introduction to #rspatial"
subtitle: "Spatial analysis with R"
author: "Andi K. Herlan"
date: "2016/12/28"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

class: left, middle

Hello!

I'm Andi.

Nice to meet you.

---
class: inverse, center, middle

# Get Started

---

# Overview

- Basic methods and classes in R of spatial analysis:

  - **sf** and **sp** packages
  
  - **raster**, and more...

- Advanced visualization

- Working with spatial database, huge raster data, and so on...

---
class: inverse, middle, center

# Vector data

---

## Why **sf** rather than **sp**

Really, **sp** is not bad at all! But **sf** ...

--

using dataframe class sf, GIS GUI app user friendly, attribute table alike

.pull-left[
untuk contoh R di sebelah kiri
]

.pull-right[
untuk contoh QGIS di sebelah kanan
]

--

and loves **dplyr**!

.footnote[I'm not a fan of tidyverse but it is insanely usefull]

---

## **sf** package

The **sf** package in R is an implementation of simple features. Merujuk pada spatial data class di R, and the package itself.

```{r}
# install.packages("sf")
```

But...

--

Firsly, install dependencies (especially on MacOSX and Linux):

- GEOS
- GDAL
- PROJ

```{r}
library("sf")
```

See ... for more details.

---

## **sf** package (cont.)

Most of the functions start with prefix `st_`

---

## Reading vector data

Bisa membaca berbagai macam format yang umum digunakan seperti *.shp* (dkk) dan *.gpkg* misalnya.

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

Berikan contoh kedua dengan data gpkg.

---

## Map plot

Plot dengan base dan ggplot2

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

## Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---
class: inverse, middle, center

# Advanced Visualization

---

## Leaflet

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
```

---

## Contoh menulis highlighted code

An example of using the trailing comment `#<<` to highlight lines:

```{r tidy=FALSE, eval=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---
background-image: url(`r xaringan:::karl`)
background-size: cover
class: center, bottom, inverse

## Haha

---

class: inverse, center, middle

# Thanks!

Twitter: [**@terusterang__**](https://twitter.com/terusterang__)

Github: [**akherlan**](https://github.com/akherlan)

---
class: center, middle

# Gabung!

### Telegram Group Komunitas R Indonesia
[**@GNURIndonesia**](https://t.me/GNURIndonesia)
